---
title: "Quarto Shiny: Interactive Analytics Dashboard"
author: "Lavish Analyst"
format: 
  html:
    theme: cosmo
    toc: true
server: shiny
---

## Introduction

This is an interactive Quarto document utilizing R Shiny. The user can interactively customize parameters of the data analysis and see the visualizations update in real time.

## Interactive Distribution Plot

Adjust the controls below to generate normal random variables and visualize their distribution.

```{r}
#| panel: sidebar
library(echarts4r)
sliderInput("obs", "Number of observations:", 
            min = 10, max = 1000, value = 500, step = 10)

selectInput("color", "Plot Color:",
            choices = c("Modern Purple" = "#8b5cf6", "Red" = "red", "Steel Blue" = "steelblue", "Tomato" = "tomato", "Forest Green" = "forestgreen", "Goldenrod" = "goldenrod"),
            selected = "#8b5cf6")

checkboxInput("density", "Show Density Curve", value = TRUE)
```

```{r}
#| panel: fill
echarts4rOutput("distPlot")
```

```{r}
#| context: server
library(echarts4r)
library(dplyr)

output$distPlot <- renderEcharts4r({
  
  data <- rnorm(input$obs)
  df <- data.frame(val = data)
  
  p <- df %>%
    e_charts() %>%
    e_histogram(val, name = "Histogram") %>%
    e_color(c(input$color, "darkblue")) %>%
    e_y_axis(name = "Count") %>%
    e_title(paste("Histogram of", input$obs, "Normal Observations")) %>%
    e_tooltip(trigger = "axis")
  
  if (input$density) {
    p <- p %>%
      e_density(val, name = "Density", y_index = 1, smooth = TRUE) %>%
      e_y_axis(index = 1, name = "Density", show = TRUE)
  }
  p
})
```

## Summary Statistics

Below is a summary of the generated dataset.

```{r}
tableOutput("statsTable")
```

```{r}
#| context: server
output$statsTable <- renderTable({
  data <- rnorm(input$obs)
  data.frame(
    Metric = c("Min", "Mean", "Median", "Max", "SD"),
    Value = c(min(data), mean(data), median(data), max(data), sd(data))
  )
})
```
